quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-10 paper-quollr.Rmd
Updated link plots

scurve_umap_model_vis <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from_reindexed,
                         lineTo = tr_from_to_df_scurve$to_reindexed,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "400px", height = "380px")

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from_reindexed,
                         lineTo = tr_from_to_df_scurve$to_reindexed,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "400px", height = "380px")

@@

nldrdt_link
```

@@

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "370px", height = "370px")

>>>>

scurve_umap_model_vis <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "400px", height = "380px")

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "400px", height = "380px")

@@

crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;
    height: 380px;
    width: 500px",
        nldrdt_link
    ),
    device = "xs"
)
```

@@

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from,
                                               lineTo = edge_data$to,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "370px", height = "370px")
